---
title: "P8105_HW1_jao2195"
output: github_document
---

# Problem 1.1 - Install Packages / Load Libraries

This problem focuses the use of inline R code, plotting, and the behavior of ggplot for variables of different types.

Use the code below to download the a package containing the early_january_weather dataset:

install.packages("moderndive").

You only need to run this command once to install the package, and you can do so directly in the console. This code shouldn’t be executed by your RMarkdown file.

Load the moderndive library, and use the following code to load the early_january_weather dataset:

```{r, message=FALSE}
#1. Installing Packages and Libraries 

#
#Loading Libraries
library(moderndive)
library(tidyverse)
library(ggplot2)

#2. Loading early_january_weather dataset from moderndive package.

data(early_january_weather)

#3. Looking at help function to learn more about the variables in the dataset. 
help(early_january_weather)

```
# Problem 1.2 - Inline R code Dataset Discussion Short Description

Write a short description of the dataset using inline R code accessing the dataset help file can be informative. In your discussion, please include:

*the variables in this dataset, including names / values of important variables
*the size of the dataset (using nrow and ncol)
*the mean temperature

################################################################################
# My Short Description of Early January Weather Dataset

The Early January Weather data (early_january_weather) is a dataset that contains hourly meterological data for Laguardia (LGA), John F. Kennedy (JFK) N, and Newark (EWR) Airports in the New York City area. This data is a subset of the nycflights13 dataset in R.  This dataset contains `r ncol(early_january_weather)` variables: `r colnames(early_january_weather)` and `r nrow(early_january_weather)` observations. Values of importat variables in the dataset include: Average Preciptation, which was `r mean(pull(early_january_weather, precip))` inches. Maximum visibility in early January was `r max(pull(early_january_weather,visib))` miles. The mean (average) temperature in early January 2013 was `r round(mean(pull(early_january_weather, temp)))` degrees Fahrenheit !

################################################################################

# Problem 1.3 - Creating Scatterplot of Humidity/Temperature Over Time

Make a scatterplot of temp (y) vs time_hour (x); color points using the humid variable (adding color = ... inside of aes in your ggplot code should help). Describe patterns that are apparent in this plot.
Export your scatterplot to your project directory using ggsave.

################################################################################
# My Short Description of the Scatterplot 


```{r}
#Creating Scatterplot, storing in myplot object.
myplot <-
  ggplot(early_january_weather) + 
  geom_point(aes(x= time_hour, y = temp, col= humid)) + 
  labs(x="Time", y="Temperature (Fahrenheit, F)", col="Relative Humidity", title="Temperature vs. Humidity ") 

#Printing myplot object to rendered document.
myplot

#Saving .png file version to plot to working directory (wd).
ggsave("Temp_Humid_Scatterplot_Problem 1.png") 

```
