---
title: "P8105_HW1_jao2195"
output: github_document
---

# Problem 1

This problem focuses the use of inline R code, plotting, and the behavior of `r ggplot` for variables of different types.

Use the code below to download the a package containing the `r penguins` dataset:

`r install.packages("moderndive")`

You only need to run this command once to install the package, and you can do so directly in the console. This code shouldn’t be executed by your RMarkdown file.

Load the `r moderndive` library, and use the following code to load the early_january_weather dataset:

```{r}
#1. Installing Packages and Libraries 
#install.packages("moderndive")  #Commented out install so it does not execute in github rendering.
library(moderndive)
library(tidyverse)
library(knitr)
library(ggplot2)

#2. Loading early_january_weather dataset from moderndive package. Storing in variable called weather.

weather <- data("early_january_weather")

```

Write a short description of the dataset using inline R code; accessing the dataset help file can be informative. In your discussion, please include:

the variables in this dataset, including names / values of important variables
the size of the dataset (using nrow and ncol)
the mean temperature
Make a scatterplot of temp (y) vs time_hour (x); color points using the humid variable (adding color = ... inside of aes in your ggplot code should help). Describe patterns that are apparent in this plot.

Export your scatterplot to your project directory using ggsave.

```{r}

```


```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.